HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
edits

\begin{figure*}
  \begin{adjustbox}{trim=2.3cm 0 0 0}
  \begin{tikzpicture}
    [level 1/.style={sibling distance=7.5em},
      level 2/.style={sibling distance=5em},
      level 3/.style={sibling distance=5em},
      level 4/.style={sibling distance=3em}]
    %[semithick, x=2.4cm,y=0.8cm, >=latex, baseline=7ex,
    %  inner sep=.3ex, outer sep=.7ex, minimum size=1.2ex,->]
  \node (ROOT) [label={B}] [fill=blue, circle] {}
  child {node (H3) [label={A}] [fill=yellow,circle] {}
    child {node [label={[red]:R}] {Golf} edge from parent node[left] {}}
    child {node (H1) [label={[orange]30:O}] [fill=orange,circle] {}
      child {node [label={}] {became} edge from parent node[left]  {}}
      child {node [label={}] {a} edge from parent node[left]  {}}
      child {node [label={}] {passion} edge from parent node[left]  {}}
    }
    child {node (H2) [label={A}] [fill=yellow,circle] {}
      child {node {} edge from parent[draw=none] {}}
      child {node {} edge from parent[draw=none] {}}
      child {node {} edge from parent[draw=none] {}}
      child {node {} edge from parent[draw=none] {}}
      child {node [label={[red]:R}] {for} edge from parent node[left]  {}}
      child {node [label={[green]:G}] {his} edge from parent node[left]  {}}
      child {node [label={[orange]:O}] {oldest} edge from parent node[left]  {}}
      child {node [label={[green]:G}] {daughter} edge from parent node[left]  {}}
    }
  }
  child {node {} edge from parent[draw=none] {}}
  child {node (H4) [label={[]30:A}] [fill=yellow,circle] {}
    child {node (she) [label={[green]:G}] {she} edge from parent node[left]  {}}
    child {node [label={[green]:G}] {attended} edge from parent node[left]  {}}
    child {node [label={[green]:G}] {daily} edge from parent node[left]  {}}
    child {node [label={[green]:G}] {lessons} edge from parent node[left]  {}}
  }
  child {node [label={[red]:R}] {and} edge from parent node[left]  {}}
  child {node (H5) [label={A}] [fill=yellow,circle] {}  
    child {node [label={[red]:R}] {greatly} edge from parent node[left] {}}
    child {node [label={[orange]:O}] {improved} edge from parent node[left] {}}
  };
  \draw[dashed] (H5) -> (she) ;

  \com{
  child {node (H1) [label={\#8}] [fill=black,circle] {}
    child {node [label={\#2}] {graduation} edge from parent node[right] {$P$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    }
    child {node (H2) [label={\#9}] [fill=black,circle] {}
      child {node  {} edge from parent[draw=none]}
      child {node  {} edge from parent[draw=none]}
      child {node [label={\#3}] (Tom) {Tom} edge from parent node[right] {$A$}}
      child {node [label={\#4}] {moved} edge from parent node[right] {$P$}}
      child {node [label={\#10}] [fill=black,circle] {}
        child {node [label={\#5}] {to} edge from parent node[right] {$R$}}
        child {node [label={\#6}] {NYC} edge from parent node[right] {$C$}}
        edge from parent node[right] {$A$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    };
    \draw (H1) -> (Tom) node[midway, right] {$A$ \hspace{0.2cm}};
    }
  \end{tikzpicture}
  \\
  \end{adjustbox}
  \adjustbox{width=\textwidth,center,margin=.5em}{\it His old daughter loved tennis, and took daily lessons however good he was}

@@

A design principle of HMEANT states that
if the translation cannot be annotated with verbal argument structure
(for whatever reason, including incomprehensibility), it cannot convey the meaning,
while HUME does not share this theoretical commitment.
For instance, consider the sentence ``a coronary angioplasty may not be technically possible'',
and the translation ``eine koronare Angioplastie kann nicht technisch m{\"o}glich''
(lit. ``a coronary angioplasty can not technically possible''),
produced by an MT system in our experiments.
The translation is correct, except that the main verb ``sein'' (``be'') is omitted.
While this may be interpreted is a minor error, HMEANT will assign it a very low score,
as it failed to translate the main verb.

However, HMEANT's independent annotation of the source and translation makes a stricter check
of whether the translation can be understood.
than we do. HUME may be artificially boosting the perceived understandability of
the sentence by allowing access to the source.

>>>>

\begin{figure*}
  \begin{adjustbox}{trim=2.3cm 0 0 0}
%   \begin{tikzpicture}
%     [level 1/.style={sibling distance=7.5em},
%       level 2/.style={sibling distance=5em},
%       level 3/.style={sibling distance=5em},
%       level 4/.style={sibling distance=3em}]
%     %[semithick, x=2.4cm,y=0.8cm, >=latex, baseline=7ex,
%     %  inner sep=.3ex, outer sep=.7ex, minimum size=1.2ex,->]
%   \node (ROOT) [label={B}] [fill=blue, circle] {}
%   child {node (H3) [label={A}] [fill=yellow,circle] {}
%     child {node [label={[red]:R}] {Golf} edge from parent node[left] {}}
%     child {node (H1) [label={[orange]30:O}] [fill=orange,circle] {}
%       child {node [label={}] {became} edge from parent node[left]  {}}
%       child {node [label={}] {a} edge from parent node[left]  {}}
%       child {node [label={}] {passion} edge from parent node[left]  {}}
%     }
%     child {node (H2) [label={A}] [fill=yellow,circle] {}
%       child {node {} edge from parent[draw=none] {}}
%       child {node {} edge from parent[draw=none] {}}
%       child {node {} edge from parent[draw=none] {}}
%       child {node {} edge from parent[draw=none] {}}
%       child {node [label={[red]:R}] {for} edge from parent node[left]  {}}
%       child {node [label={[green]:G}] {his} edge from parent node[left]  {}}
%       child {node [label={[orange]:O}] {oldest} edge from parent node[left]  {}}
%       child {node [label={[green]:G}] {daughter} edge from parent node[left]  {}}
%     }
%   }
%   child {node {} edge from parent[draw=none] {}}
%   child {node (H4) [label={[]30:A}] [fill=yellow,circle] {}
%     child {node (she) [label={[green]:G}] {she} edge from parent node[left]  {}}
%     child {node [label={[green]:G}] {attended} edge from parent node[left]  {}}
%     child {node [label={[green]:G}] {daily} edge from parent node[left]  {}}
%     child {node [label={[green]:G}] {lessons} edge from parent node[left]  {}}
%   }
%   child {node [label={[red]:R}] {and} edge from parent node[left]  {}}
%   child {node (H5) [label={A}] [fill=yellow,circle] {}  
%     child {node [label={[red]:R}] {greatly} edge from parent node[left] {}}
%     child {node [label={[orange]:O}] {improved} edge from parent node[left] {}}
%   };
%   \draw[dashed] (H5) -> (she) ;
% 
%   \com{
%   child {node (H1) [label={\#8}] [fill=black,circle] {}
%     child {node [label={\#2}] {graduation} edge from parent node[right] {$P$}}
%       %child {node {to Paris} edge from parent node[right] {$A$}}
%       edge from parent node[left] {$H$}
%     }
%     child {node (H2) [label={\#9}] [fill=black,circle] {}
%       child {node  {} edge from parent[draw=none]}
%       child {node  {} edge from parent[draw=none]}
%       child {node [label={\#3}] (Tom) {Tom} edge from parent node[right] {$A$}}
%       child {node [label={\#4}] {moved} edge from parent node[right] {$P$}}
%       child {node [label={\#10}] [fill=black,circle] {}
%         child {node [label={\#5}] {to} edge from parent node[right] {$R$}}
%         child {node [label={\#6}] {NYC} edge from parent node[right] {$C$}}
%         edge from parent node[right] {$A$}}
%       %child {node {to Paris} edge from parent node[right] {$A$}}
%       edge from parent node[left] {$H$}
%     };
%     \draw (H1) -> (Tom) node[midway, right] {$A$ \hspace{0.2cm}};
%     }
%   \end{tikzpicture}
  \\
  \end{adjustbox}
  \adjustbox{width=\textwidth,center,margin=.5em}{\it His old daughter loved tennis, and took daily lessons however good he was}

@@

A design principle of HMEANT states that
if the translation cannot be annotated with verbal argument structure
(for whatever reason, including incomprehensibility), it cannot convey the meaning,
while HUME does not share this theoretical commitment.
For instance, consider the sentence ``a coronary angioplasty may not be technically possible'',
and the translation ``eine koronare Angioplastie kann nicht technisch m{\"o}glich''
(lit. ``a coronary angioplasty can not technically possible''),
produced by an MT system in our experiments.
The translation is correct, except that the main verb ``sein'' (``be'') is omitted.
While this may be interpreted as a minor error, HMEANT will assign it a very low score,
as it failed to translate the main verb.

However, HMEANT's independent annotation of the source and translation makes a stricter check
of whether the translation can be understood
than we do. HUME may be artificially boosting the perceived understandability of
the sentence by allowing access to the source.
